---
title: "Homework 5"
author: Fiona Ehrich
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

First, I will take a look at the raw data.

```{r message = FALSE, warning = FALSE}
homicide_df = read_csv("homicide_data/homicide-data.csv")

homicide_df
```

The raw dataset has `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns. Each row corresponds to a homicide case and provides the following information regarding the given case: id number, date reported, victim first & last name, victim race, victim age, victim sex, city & state, latitude & longitude, and disposition (eg, "Closed by arrest").

Now I will create a `city_state` variable.

```{r message = FALSE, warning = FALSE}
homicide_df =
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

I will now summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r message = FALSE, warning = FALSE}
aggregate_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Next, I will use the `prop.test` function to estimate the proportion of homicides that are unsolved for Baltimore, MD.

```{r}
baltimore_df =
  prop.test(
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
    )

baltimore_df %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

Now, I will run `prop.test` for each of the cities in the dataset and extract both the proportion of unsolved homicides and the confidence intervals for each.

```{r}
results_df =
  aggregate_df %>% 
  mutate(
    prop_tests = map2(
      .x = hom_unsolved,
      .y = hom_total,
      ~prop.test(x = .x, n = .y)
      ),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Below is a plot showing the estimates and CIs for each city.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Estimated Proportion of Unsolved Homicides by City",
    x = "City_State",
    y = "Estimated Proportion of Unsolved Homicides"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
